---
title: "Prediction Assignment Writeup"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the data to mmemory
```{r load}
traindata <- read.csv('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv', na.strings = c("", "NA"))
testdata <-read.csv('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv', na.strings = c("", "NA"))
# head(traindata)
# head(testdata)
# names(traindata) == names(testdata)
```

## Data Preprocessing

Remove the columns which NAs are above 50%. Remove unnecessary variables. 

```{r clean}
traindata = traindata[,-(1:7)]
testdata = testdata[,-(1:7)]
testdata = testdata[,-ncol(testdata)]
sum(colSums(is.na(traindata)) == 0)

badcol = c()
for (i in names(traindata)){
    if(mean(is.na(traindata[,i])) > .5){
        badcol = c(badcol,i)
    }
}
# badcol
library(dplyr)
traindata = select(traindata, -c(badcol))
testdata = select(testdata, -badcol)
```

## Split the data into training and test ones

```{r split}
set.seed(2021)
library(caret)
inTrain = createDataPartition(y = traindata$classe, p = .7, list = FALSE)
training = traindata[inTrain,]
testing = traindata[-inTrain,]
dim(training)
dim(testing)
```


```{r para, echo = FALSE}
library(parallel)
library(doParallel)
cl <- makeCluster(detectCores() - 2)
registerDoParallel(cl)
```

## Set Cross Validation up

```{r cv}
ctrl = trainControl(method="cv", number=5, verboseIter=FALSE, allowParallel = T)
```

## Run Models and get the Accuracy
### Random Forest
```{r rf}
modrf = train(classe ~ ., data = training, method = 'rf', trControl = ctrl)
predrf = predict(modrf, testing)
confusionMatrix(predrf, factor(testing$classe))$overall["Accuracy"]
```
### Linear Discriminant Analysis
```{r lda}
modlda = train(classe ~. , data = training, method = 'lda', trControl = ctrl)
predlda = predict(modlda, testing)
confusionMatrix(predlda, factor(testing$classe))$overall["Accuracy"]
```

### Recurisive Partitioning and Regression Trees
```{r rpart}
modrpart = train(classe ~., data = training, method = 'rpart', trControl = ctrl)
predrpart = predict(modrpart, testing)
confusionMatrix(predrpart, factor(testing$classe))$overall["Accuracy"]
```

### Generalized Boosted Model (GBM)
```{r gbm}
modgbm = train(classe ~., data = training, method = 'gbm', trControl = ctrl, verbose = FALSE)
predgbm = predict(modgbm, testing)
confusionMatrix(predgbm, factor(testing$classe))$overall["Accuracy"]
```

According to the accuracy of 4 different models, the random Foresst model predicts best.

## Get the Final Prediction

```{r prediction}
finalpred = predict(modrf, newdata = testdata)
print(finalpred)

```

```{r close, echo = FALSE}
# close multicores
stopCluster(cl)
```